Synthesizing Symmetric Lenses

### 2018-07-07 papers/SymmetricLenses/main.tex
Still stuck... urgh

V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s) &= \{t \in \mathcal{L}(T_1 \; |_q \; T_2) \; | \;  \MergeLOf{\Lens_1}{\Lens_2}.\PutROf{s}{t} = t\}\\
&= \{t \in \mathcal{L}(T_1 \; |_q \; T_2) \; | \;  \ell_1.\PutROf{s}{t} = t \text{ or } \ell_2.\PutROf{s}{t} = t\}\\
&= V_{\ell_1}(s) \cup V_{\ell_2}(s)
First we consider $H(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))$:

@@

@@

&= \frac{q * P_{T_1}(V_{\ell_1}(s)) \left[\log_2 q + \log_2 \left[\frac{P_{T_1}(V_{\ell_1}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] - H(V_{\ell_1}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\\
&+ \frac{(1-q) * P_{T_2}(V_{\ell_2}(s)) \left[\log_2 (1-q) + \log_2 \left[\frac{P_{T_2}(V_{\ell_2}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] - H(V_{\ell_2}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}

@@

>>>>

Observe that 
\begin{align*}
V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s) &= \{t \in \mathcal{L}(T_1 \; |_q \; T_2) \; | \;  \MergeLOf{\Lens_1}{\Lens_2}.\PutROf{s}{t} = t\}\\
&= \{t \in \mathcal{L}(T_1 \; |_q \; T_2) \; | \;  \ell_1.\PutROf{s}{t} = t \text{ or } \ell_2.\PutROf{s}{t} = t\}\\
&= V_{\ell_1}(s) \cup V_{\ell_2}(s)
\end{align*}
To compute $H(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))$, we use the formula 
$$H(P_1, P_2) = H(m(P_1), m(P_2)) + m(P_1)H\left(\frac{P_1}{m(P_1)}\right) + m(P_2)H\left(\frac{P_2}{m(P_2)}\right)$$
if the probability space $P$ is the sum of measure spaces $P_1$ and $P_2$, and $m(P_i)$ is the measure of $P_i$:
\begin{align*}
&H(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)) = H \left(\frac{q * P_{T_1}V_{\ell_1}(s)}{P_{T_1 \; |_q \; T_2}{V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}}, \frac{(1-q) * P_{T_2}V_{\ell_2}(s)}{P_{T_1 \; |_q \; T_2}{V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}}\right)\\
&= \frac{q * P_{T_1}V_{\ell_1}(s)}{P_{T_1 \; |_q \; T_2}{V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}} H(V_{\ell_1}(s)) + \frac{(1-q) * P_{T_2}V_{\ell_2}(s)}{P_{T_1 \; |_q \; T_2}{V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s)}} H(V_{\ell_2}(s))
\end{align*}

\iffalse

@@

Consequently,

@@

&= \frac{q * P_{T_1}(V_{\ell_1}(s)) \left[\log_2 \left[\frac{q * P_{T_1}(V_{\ell_1}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] - H(V_{\ell_1}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\\
&+ \frac{(1-q) * P_{T_2}(V_{\ell_2}(s)) \left[\log_2 \left[\frac{(1-q) * P_{T_2}(V_{\ell_2}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] - H(V_{\ell_2}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}

@@

\fi
